Patient-Specific Neural Field Modeling from Mirco-Electrode Data

### 2010-07-22 ltx/data_paper/DataPaper.tex
rearranged the m-step a little more in an effort to make it clearer

The algorithm for the modified URTSS can be seen in Figure~\ref{tab:URTSSAlgorithm}.

@@

 \mathcal Q(\boldsymbol \theta,\xi,\boldsymbol\theta',\xi')&=\mathbf E_{\boldsymbol (\theta',\xi')}\left[\ln p(\mathbf X,\mathbf Y;\boldsymbol \theta,\xi)\right]\nonumber\\

@@

where $ \mathbf E_{\boldsymbol (\theta',\xi')}$ denotes expectation taken with respect to the distribution $p(\mathbf X | \mathbf Y;\boldsymbol \theta',\xi') $ where $\boldsymbol \theta'$ and $\xi'$are the current parameter estimates. It should be noted that

@@

@@

	\beta &= \sum_{t=1}^T\mathbf E_{(\theta',\xi')}\left[ \ln \alpha-\mathbf x_{t+1}^\top\boldsymbol\Sigma_w^{-1}\mathbf x_{t+1}\right] \\

@@

\Xi_1&=\mathbf E[\sum_{t=1}^T\mathbf x_t\mathbf x_{t+1}^\top] \\
\Xi_2&=\sum_{t=1}^T\Lambda_t(\mathbf r')\mathbf P_t \tilde{\Lambda}_t(\mathbf r')

@@

is constant with respect to $\boldsymbol \theta$ and will disappear by differentiation, and
\begin{equation}\label{eq:Xi0}
 \Xi_0=\sum_{t=1}^T\left[ \mathbf{\hat x}_{t+1}^\top\boldsymbol\Sigma_e^{-1}q(\mathbf{\hat x}_t)+\int_\Omega\boldsymbol \phi^\top(\mathbf r') \mathbf M_t \boldsymbol\Sigma_e^{-1}  \boldsymbol{\Psi}(\mathbf{r}') f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t) d\mathbf{r}'\right] 
\begin{equation}\label{eq:Xi1}
 \Xi_1=\mathbf E[\sum_{t=1}^T\mathbf x_t\mathbf x_{t+1}^\top] 
 \Xi_2=\sum_{t=1}^T\Lambda_t(\mathbf r')\mathbf P_t\tilde{\Lambda}_t(\mathbf r')
 \Lambda(\mathbf r')=\begin{bmatrix}\boldsymbol \lambda_1(\mathbf r') & \boldsymbol \lambda_2(\mathbf r')& \dots &\boldsymbol \lambda_i(\mathbf r')\end{bmatrix} \quad \text{and} \quad \tilde{\Lambda}(\mathbf r')=\begin{bmatrix}\tilde{\boldsymbol \lambda}_1(\mathbf r') \\ \tilde{\boldsymbol \lambda}_2(\mathbf r') \\ \vdots \\ \tilde{\boldsymbol \lambda}_i(\mathbf r')\end{bmatrix}
and where
 \boldsymbol\lambda_i(\mathbf r')=\int \boldsymbol \Psi^\top(\mathbf r')\boldsymbol \Sigma_e^{-1}\phi_i(\mathbf r')f'(\boldsymbol\phi^\top(\mathbf r')\mathbf x_t)d\mathbf r'

@@

 \tilde{\boldsymbol \lambda}_i(\mathbf r')=\int \boldsymbol \Psi(\mathbf r')\phi_i(\mathbf r')f'(\boldsymbol\phi^\top(\mathbf r')\mathbf x_t)d\mathbf r'
 \Xi_3=\sum_{t=1}^T\left[ \mathbf{\hat x}_{t}^\top\boldsymbol\Sigma_e^{-1}q(\mathbf{\hat x}_t)+\int_\Omega\boldsymbol \phi^\top(\mathbf r') \mathbf P_t \boldsymbol\Sigma_e^{-1}  \boldsymbol{\Psi}(\mathbf{r}') f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t) d\mathbf{r}'\right] 
 \Xi_4=\mathbf E[\sum_{t=1}^T\mathbf x_t\mathbf x_{t}^\top]
differentiate with respect to $\boldsymbol\theta$ and $\xi$ and equating to zero we get

@@

 \xi=\frac{tr\left\lbrace \Xi_1 \boldsymbol\Sigma_e^{-1}\right\rbrace-\Xi_3\Xi_2^{-\top}\Xi_0^\top}{tr\left\lbrace \Xi_4 \boldsymbol\Sigma_e^{-1}\right\rbrace-\Xi_3\Xi_2^{-\top}\Xi_3^\top}

>>>>

The algorithm for the modified URTSS can be seen in Table~\ref{tab:URTSSAlgorithm}.

@@

 \mathcal Q(\boldsymbol \theta,\xi,\boldsymbol\theta',\xi')&=\mathbf E_{\boldsymbol (\theta',\xi')}\left[\ln p(\mathbf X,\mathbf Y;\boldsymbol \theta,\xi)\right] \\

@@

\dean{there is a parameter missing here..} where $ \mathbf E_{\boldsymbol (\theta',\xi')}$ denotes expectation taken with respect to the distribution $p(\mathbf X | \mathbf Y;\boldsymbol \theta',\xi') $ where $\boldsymbol \theta'$ and $\xi'$are the current parameter estimates. It should be noted that

@@

\begin{align}\label{eq:Voldermont}

@@

	\beta &= \sum_{t=1}^T\mathbf E_{(\theta',\xi')}\left[ \ln \alpha-\mathbf x_{t+1}^\top\boldsymbol\Sigma_w^{-1}\mathbf x_{t+1}\right] \label{eq:def of beta} \\

@@

\Xi_1&=\mathbf E\left[\sum_{t=1}^T\mathbf x_t\mathbf x_{t+1}^\top\right] \\
\Xi_2&=\sum_{t=1}^T\Lambda_t(\mathbf r')\mathbf P_t \tilde{\Lambda}_t(\mathbf r') \\
 \Xi_3&=\sum_{t=1}^T\left[ \mathbf{\hat x}_{t}^\top\boldsymbol\Sigma_e^{-1}q(\mathbf{\hat x}_t)+\int_\Omega\boldsymbol \phi^\top(\mathbf r') \mathbf P_t \boldsymbol\Sigma_e^{-1}  \boldsymbol{\Psi}(\mathbf{r}') f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t) d\mathbf{r}'\right] \\
 \Xi_4&=\mathbf E\left[\sum_{t=1}^T\mathbf x_t\mathbf x_{t}^\top\right]

@@

@@

	 \Lambda(\mathbf r')&=\begin{bmatrix}\boldsymbol \lambda_1(\mathbf r') & \boldsymbol \lambda_2(\mathbf r')& \dots &\boldsymbol \lambda_i(\mathbf r')\end{bmatrix} \\
	 \boldsymbol\lambda_i(\mathbf r')&=\int \boldsymbol \Psi^\top(\mathbf r')\boldsymbol \Sigma_e^{-1}\phi_i(\mathbf r')f'(\boldsymbol\phi^\top(\mathbf r')\mathbf x_t)d\mathbf r'\\
	\tilde{\Lambda}(\mathbf r')&=\begin{bmatrix}\tilde{\boldsymbol \lambda}_1(\mathbf r') \\ \tilde{\boldsymbol \lambda}_2(\mathbf r') \\ \vdots \\ \tilde{\boldsymbol \lambda}_i(\mathbf r')\end{bmatrix} \\
	 \tilde{\boldsymbol \lambda}_i(\mathbf r')&=\int \boldsymbol \Psi(\mathbf r')\phi_i(\mathbf r')f'(\boldsymbol\phi^\top(\mathbf r')\mathbf x_t)d\mathbf r'
When taking the derivative of equation~\ref{eq:Voldermont}, the first term described in equation~\ref{eq:def of beta} will will disappear. Also, when we differentiate with respect to $\boldsymbol\theta$ and $\xi$ and equating it to zero we get

@@

 \xi=\frac{tr\left\lbrace \Xi_1 \boldsymbol\Sigma_e^{-1}\right\rbrace-\Xi_3\Xi_2^{-\top}\Xi_0^\top}{tr\left\lbrace \Xi_4 \boldsymbol\Sigma_e^{-1}\right\rbrace-\Xi_3\Xi_2^{-\top}\Xi_3^\top}.
